---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: 
  - paperwidth=11in
  - paperheight=8.5in
  - margin=0.05in 
 
header-includes:
  \usepackage{fontspec}
  \setmainfont{Calibri}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{C:/Users/tdmed/OneDrive/_Github/boomers-analytics/www}}

---

```{r setup, include=FALSE}
# classoption: landscape
library(DT)
# webshot::install_phantomjs()
library(webshot)
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(flextable)
# library(pandoc)
library(ggplot2)
opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(fig.pos = '!h')

```
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=1.5cm, height=1.5cm]{Schaumburg}
\end{minipage}
\hfill 
\begin{minipage}{0.5\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont Schaumburg Boomers Hitting Stats}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=2.5cm, height=1.5cm]{fllogo2}
\end{minipage}

\vspace{-5mm} 
\begin{center}
\textbf{\normalsize Standard Batting}
\end{center}
\vspace{-5mm} 
```{r, hitters-standard_boom, echo=FALSE, warning=FALSE, fig.align='center'}
hit_std_boom %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
    row_spec(row = 0, color = "white",background = "#12294b", bold = TRUE) %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(hit_std_boom), border_right = TRUE)  
```
\begin{center}
\textbf{\normalsize Advanced Batting}
\end{center}
\vspace{-5mm} 
```{r, hitters-advanced_boom, echo=FALSE, warning=FALSE, fig.align='center'}
hit_adv_boom %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(hit_adv_boom), border_right = TRUE) 
```


\newpage 


\begin{center}
\textbf{\normalsize vs RHP}
\end{center}
\vspace{-6mm} 
```{r, hitters-splits_boom_R, echo=FALSE, warning=FALSE, fig.align='center'}
hit_splits_boom_RHP %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(11,  border_left = TRUE) %>%
  column_spec(ncol(hit_splits_boom_RHP), border_right = TRUE) # %>%
 # add_header_above(c(" " = 1, "vs RHP" = 9, "vs LHP" = 9),color = "black", background = "#FF5600", font_size = 10, bold = TRUE) 
```

\begin{center}
\textbf{\normalsize vs LHP}
\end{center}
\vspace{-6mm} 
```{r, hitters-splits_boom_L, echo=FALSE, warning=FALSE, fig.align='center'}
hit_splits_boom_LHP %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(11,  border_left = TRUE) %>%
  column_spec(ncol(hit_splits_boom_LHP), border_right = TRUE) # %>%
 # add_header_above(c(" " = 1, "vs RHP" = 9, "vs LHP" = 9),color = "black", background = "#FF5600", font_size = 10, bold = TRUE) 
```

\begin{center}
\textbf{\normalsize BattedBall}
\end{center}
\vspace{-6mm} 
```{r, hitters-battedball_boom, echo=FALSE, warning=FALSE, fig.align='center'}
hit_bb_boom %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center") %>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(hit_bb_boom), border_right = TRUE)   

```


\newpage 


\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=1.5cm, height=1.5cm]{Schaumburg}
\end{minipage}
\hfill 
\begin{minipage}{0.5\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont Schaumburg Boomers Pitching Stats}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=2.5cm, height=1.5cm]{fllogo2}
\end{minipage}

\vspace{-5mm} 

\textbf{\normalsize Standard}
\begin{center}
\end{center}
\vspace{-5mm} 
```{r, pitchers-standard_boom, echo=FALSE, warning=FALSE, fig.align='center'}
pitch_std_boom %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(pitch_std_boom), border_right = TRUE)  
```

\begin{center}
\textbf{\normalsize Advanced}
\end{center}
\vspace{-5mm} 

```{r, pitchers-advanced_boom, echo=FALSE, warning=FALSE, fig.align='center'}
pitch_adv_boom %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(pitch_adv_boom), border_right = TRUE)  
```

\newpage 

\begin{center}
\textbf{\normalsize vs RHH}
\end{center}
\vspace{-6mm} 
```{r, pitcher-splits_boom_R, echo=FALSE, warning=FALSE, fig.align='center'}
pitch_splits_boom_RHP %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(12,  border_left = TRUE) %>%
  column_spec(ncol(pitch_splits_boom_RHP), border_right = TRUE)
```

\begin{center}
\textbf{\normalsize vs LHH}
\end{center}
\vspace{-6mm} 
```{r, pitcher-splits_boom_L, echo=FALSE, warning=FALSE, fig.align='center'}
pitch_splits_boom_LHP %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(12,  border_left = TRUE) %>%
  column_spec(ncol(pitch_splits_boom_LHP), border_right = TRUE)  
```

\newpage

\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=1.5cm, height=1.5cm]{`r params$opp_loc`}
\end{minipage}
\hfill 
\begin{minipage}{0.5\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont `r params$team_filter` Hitting Stats }
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=2.5cm, height=1.5cm]{fllogo2}
\end{minipage}



\begin{center}
\textbf{\normalsize Standard}
\end{center}
\vspace{-5mm} 
```{r, hitters-standard, echo=FALSE, warning=FALSE, fig.align='center'}
hit_std %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(hit_std), border_right = TRUE)  
```
\begin{center}
\textbf{\normalsize Advanced}
\end{center}
\vspace{-5mm} 
```{r, hitters-advanced, echo=FALSE, warning=FALSE, fig.align='center'}
hit_adv %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(hit_adv), border_right = TRUE) 
```


 \newpage 


\begin{center}
\textbf{\normalsize vs RHP}
\end{center}
\vspace{-6mm} 
```{r, hitters-splits_R, echo=FALSE, warning=FALSE, fig.align='center'}
hit_splits_RHP %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(11,  border_left = TRUE) %>%
  column_spec(ncol(hit_splits_RHP), border_right = TRUE)
```

 \begin{center}
\textbf{\normalsize vs LHP}
\end{center}
\vspace{-6mm} 
```{r, hitters-splits_L, echo=FALSE, warning=FALSE, fig.align='center'}
hit_splits_LHP %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(11,  border_left = TRUE) %>%
  column_spec(ncol(hit_splits_LHP), border_right = TRUE)
```

\begin{center}
\textbf{\normalsize BattedBall}
\end{center}
\vspace{-6mm} 
```{r, hitters-battedball, echo=FALSE, warning=FALSE, fig.align='center'}
hit_bb %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center") %>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(hit_bb), border_right = TRUE)   

```
 \newpage 


\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=1.5cm, height=1.5cm]{`r params$opp_loc`}
\end{minipage}
\hfill 
\begin{minipage}{0.5\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont `r params$team_filter` Pitching Stats}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=2.5cm, height=1.5cm]{fllogo2}
\end{minipage}

\vspace{-5mm} 

\begin{center}

\textbf{\normalsize Standard}

\end{center}
\vspace{-5mm} 
```{r, pitchers-standard, echo=FALSE, warning=FALSE}
pitch_std %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(pitch_std), border_right = TRUE)  
```

\begin{center}
\textbf{\normalsize Advanced}
\end{center}
\vspace{-5mm} 

```{r, pitchers-advanced, echo=FALSE, warning=FALSE}
pitch_adv %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center" )%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(ncol(pitch_adv), border_right = TRUE)  
```

\newpage 

\begin{center}
\textbf{\normalsize vs RHH}
\end{center}
\vspace{-6mm} 
```{r, pitcher-splits_R, echo=FALSE, warning=FALSE}
pitch_splits_RHH  %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(12,  border_left = TRUE) %>%
  column_spec(ncol(pitch_splits_RHH), border_right = TRUE)  
```


\begin{center}
\textbf{\normalsize vs LHH}
\end{center}
\vspace{-6mm} 
```{r, pitcher-splits_L, echo=FALSE, warning=FALSE}
pitch_splits_LHH  %>%
  kable(format = "latex",  linesep = "",  valign = 't') %>%
  kable_styling( latex_options = c("HOLD_position", 'striped'), position = "center", font_size = 9.5)%>% 
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  column_spec(12,  border_left = TRUE) %>%
  column_spec(ncol(pitch_splits_LHH), border_right = TRUE)  
```