---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
geometry:
- paperwidth=8.5in
- paperheight=11in
- margin=0.05in
header-includes:
  \usepackage{fontspec}
  \setmainfont{Calibri}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{C:/Users/tdmed/OneDrive/_Github/boomers-analytics/www}}
---
```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(pandoc)
library(ggplot2)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=1.5cm, height=1.5cm]{Schaumburg}
\end{minipage}
\hfill 
\begin{minipage}{0.5\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont Schaumburg Boomers}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=2.5cm, height=1.5cm]{fllogo2}
\end{minipage}
\vspace{-6mm} 

\begin{center}
\textbf{\normalsize  `r params_bp$cur_date_time`}
\end{center}
\vspace{-2mm} 

```{r boomers, echo = F, warning = F, fig.width = 8, fig.height = 4.5, fig.align='center'}
plot_list[[1]]
```

\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=1.5cm, height=1.5cm]{`r params_bp$away_team_loc`}
\end{minipage}
\hfill 
\begin{minipage}{0.5\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont `r params_bp$opposing_team`}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=2.5cm, height=1.5cm]{fllogo2}
\end{minipage}
\vspace{-2mm} 

```{r opponent, echo = F, warning = F, fig.width = 8, fig.height = 4.5, fig.align='center'}
if(length(plot_list) >1) {
  
  plot_list[[2]]
}
```