---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: 
  - paperwidth=8.5in
  - paperheight=11in
  - margin=0.05in 
 
header-includes:
  \usepackage{fontspec}
  \setmainfont{Calibri}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{C:/Users/tdmed/OneDrive/_Github/boomers-analytics/www}}
  
---
```{r setup, include=FALSE}
#
library(webshot)
library(tidyverse)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(flextable)
library(pandoc)
library(ggplot2)
library(cowplot)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=2cm, height=2cm]{Schaumburg}
\end{minipage}
\hfill 
\begin{minipage}{0.3\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont `r params$catcher`}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=3cm, height=2cm]{fllogo2}
\end{minipage}

\vspace{-7mm} 
\begin{center}
\textbf{\normalsize `r params$date` vs `r params$opponent`}
\end{center}
\vspace{-7mm} 
```{r strikes lost gained, echo = FALSE, warning = FALSE }
kable(catcher_summary,  format = "latex",  linesep = "") %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
  column_spec(1,border_left = TRUE) %>%
  column_spec(3, bold = T, border_left = T, color = 'white',
              background = ifelse('Game +/-' > 0 & 'Game +/-' < 3, '#93EA8E',
                                  ifelse('Game +/-' >=3,'#339a1d',
                                         ifelse('Game +/-' < 0 & 'Game +/-' > -3, '#eaa48e', '#ba1c0f')))
  ) %>%
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(ncol(catcher_summary), border_right = TRUE)
```
\vspace{-7mm}
\begin{center}
\textbf{\normalsize Frontier League Career Framing Stats}
\end{center}
\vspace{-7mm}
```{r strikes lost gained career, echo = FALSE, warning = FALSE }
kable(catcher_season_summary %>% mutate(across(3:7, ~ as.numeric(.))),  format = "latex",  linesep = "") %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
  column_spec(1,border_left = TRUE) %>%
  column_spec(7, bold = T, color = 'white',
              background =
                case_when(
                  catcher_season_summary$`+/- Strikes per Game` >= 3 ~ '#339a1d',
                  between(catcher_season_summary$`+/- Strikes per Game`, 0,3) ~ '#93EA8E',
                  between(catcher_season_summary$`+/- Strikes per Game`, 0,-3) ~ '#eaa48e',
                  catcher_season_summary$ `+/- Strikes per Game` <= -3 ~ '#ba1c0f',
                  T ~ 'white'
                  
                  
                )
              # ifelse('+/- Strikes per Game' > 0 & '+/- Strikes per Game' < 3, '#93EA8E',
              #                   ifelse('+/- Strikes per Game' >=3,'#339a1d',
              #                          ifelse('+/- Strikes per Game' < 0 & '+/- Strikes per Game' > -3, '#eaa48e', '#ba1c0f')))
  ) %>%
  row_spec(row = 0, color = "white", background = "#12294b") %>%
  column_spec(ncol(catcher_season_summary), border_right = TRUE)
```
\vspace{-5mm}
\centering
```{r strikes plots , echo = FALSE, warning = FALSE, fig.width=8, fig.height=3.5, fig.align='center'}
# grid.arrange(StolenStrikes, LostStrikes, ncol = 2)
# Create the master legend
prow <- plot_grid(
  StolenStrikes + theme(legend.position="none"),
  # NULL,
  LostStrikes + theme(legend.position="none"),
  align = 'vh',
  hjust = -1,
  nrow = 1,
  rel_widths = c(1, 1)
)

legend <- suppressWarnings(
  get_legend(
    # create some space to the left of the legend
    StolenStrikes + labs(fill = 'Pitch') +theme(#legend.box.margin = margin(0, 0, 0, 12), 
      legend.direction = 'horizontal')
  )
)


# now add in the legend
# prow + draw_grob(legend, 1/3, 0, 1/3, 1)
plot_grid(
  prow, legend,
  ncol = 1,  # Stack the plots and the legend vertically
  rel_heights = c(1, 0.1)  # Adjust height ratio to make the legend smaller
)

```
\vspace{-0.5cm}
```{r log, echo=FALSE, warning=FALSE }
if(nrow(catcher_log)>0) {
  kable(catcher_log,  format = "latex",  linesep = "") %>%
    row_spec(seq(2, nrow(catcher_log), by = 2), background = "#f2f2f2") %>%
    kable_styling(latex_options = "HOLD_position", position = "center")%>%
    column_spec(1,border_left = TRUE) %>%
    column_spec(col=9, bold = T,color = 'white',background = ifelse(catcher_log$Actual == 'BALL', '#339a1d', '#ba1c0f')) %>%
    row_spec(row = 0, color = "white", background = "#12294b") %>%
    column_spec(ncol(catcher_log), border_right = TRUE)  %>%
    column_spec(1,border_left = TRUE) 
} else {
  kable(data.frame(Message = "No Strikes Lost or Stolen!"), format = "latex", linesep = "") %>%
    kable_styling(latex_options = "HOLD_position", position = "center") %>%
    column_spec(1, border_left = TRUE) %>%
    row_spec(row = 0, color = "white", background = "#12294b") 
}
```
\newpage
\vspace{-0.5cm}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont Throwing Report}
\end{center} 




\centering
```{r tables, echo=FALSE, warning=FALSE}
if (nrow(Throwlog) >= 2) {
  kable(Throwlog, format = "latex", linesep = "") %>%
    row_spec(seq(2, nrow(Throwlog), by = 2), background = "#f2f2f2") %>%
    kable_styling(latex_options = "HOLD_position", position = "center") %>%
    column_spec(1, border_left = TRUE) %>%
    row_spec(row = 0, color = "white", background = "#12294b") %>%
    column_spec(ncol(Throwlog), border_right = TRUE)
} else if (nrow(Throwlog) == 0) {
  # Create a placeholder message if there is no data
  kable(data.frame(Message = "No Throwing Data Available"), format = "latex", linesep = "") %>%
    kable_styling(latex_options = "HOLD_position", position = "center") %>%
    column_spec(1, border_left = TRUE) %>%
    row_spec(row = 0, color = "white", background = "#12294b") 
} else {
  kable(Throwlog, format = "latex", linesep = "") %>%
    kable_styling(latex_options = "HOLD_position", position = "center") %>%
    column_spec(1, border_left = TRUE) %>%
    row_spec(row = 0, color = "white", background = "#12294b") %>%
    column_spec(ncol(Throwlog), border_right = TRUE)
}
```
\centering
```{r throwplot, echo=FALSE, warning=FALSE, fig.align='center'}
ThrowPlot
```
