---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
geometry:
- paperwidth=9in
- paperheight=12in
- margin=0.05in
header-includes:
  \usepackage{fontspec}
  \setmainfont{Calibri}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{C:/Users/tdmed/OneDrive/_Github/boomers-analytics/www}}
---
```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(pandoc)
library(ggplot2)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=1.5cm, height=1.5cm]{`r params_boom$team_logo`}
\end{minipage}
\hfill 
\begin{minipage}{0.5\textwidth}
\begin{center}
\textbf{\fontsize{24}{24}\selectfont `r params_boom$pitcher_name` PA Log}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.2\textwidth}
\centering
\includegraphics[width=2.5cm, height=1.5cm]{fllogo2}
\end{minipage}
\vspace{-6mm} 

\begin{center}
\textbf{\normalsize `r params_boom$game_date` vs. `r params_boom$opponent_team`}
\end{center}
\vspace{-6mm} 

```{r pa_tracker, results='asis', echo=FALSE, warning=FALSE, fig.align='center', include = T, fig.height=2.5  }



for (pa_i in unique(pitcher_data$PA)) {
  pa_track <- pitcher_data %>%
    filter(PA==pa_i) %>%
    mutate(#Count = glue::glue("{Balls}-{Strikes}"),
           caption = glue::glue("Inning {Inning} - PA {PA} vs. {sub('^\\\\S+\\\\s+', '', Batter)} ({BatterSide})")) %>%
    dplyr::select(`#`, Inning, Batter, BatterSide, Pitch,Velo, Count, Outs, PitchCall, PlayResult, Result, EV, LA, Dist = Distance, PlateLocSide, PlateLocHeight, hc_x, hc_y,caption, VB, HB, Spin, Tilt) %>%
    mutate(Result = str_replace_all(Result, c('Single'='1B', 'Double' = '2B', 'Triple' = '3B', 'HomeRun' ='HR', 'Error' = 'E', 'FieldersChoice' = 'FC','CatchersInterference' = 'CI', 'Sacrifice' = 'SAC')),
           PlayResult = str_replace_all(PlayResult, c('Single'='1B', 'Double' = '2B', 'Triple' = '3B', 'HomeRun' ='HR', 'Error' = 'E', 'FieldersChoice' = 'FC','CatchersInterference' = 'CI', 'Sacrifice' = 'SAC')),
    )
  
  pa_flex <- pa_track %>%
    dplyr::select(-c( PlateLocSide, PlateLocHeight, hc_x, hc_y, Inning, Batter, BatterSide,caption, PlayResult, PitchCall)) %>%
    mutate(across(c(VB,HB,EV, LA, Dist, Velo), ~ round(.,1))) %>%
    mutate(across(c(Spin), ~ round(.))) %>%
    relocate(VB,HB,Spin, Tilt, .after = Velo)
  
  caption <- tail(pa_track$caption,1)
  
  
  
  pa_zone_plot <-
    pa_zone <- ggplot(pa_track, aes(x=-PlateLocSide,y=PlateLocHeight))+
    geom_segment(data=tonybaseball::home_plate_c_pov,aes( x=x,y=y,xend=xend,yend=yend), size = 1)+
    annotate('rect', xmin = -0.78, xmax = 0.78, ymin = 1.6, ymax = 3.5, fill = 'black', color = 'black', alpha = 0.0001, linewidth = 1)+
    xlim(-2.25,2.25)+
    ylim(0,4.5)+
    coord_equal()+
    geom_point(aes(fill = Pitch), pch = 21, size = 6)+
    scale_fill_manual(values = c('FB' = 'red', 'CB' = 'darkgreen', 'SI' = '#a34700',  'SL'='#33A8FF',
                                 'CT' = 'gold',  'CH'='violet', 'OT' = 'black', 'SPL' = 'black', 'KN' = 'black',
                                 'Fastball' = 'red', 'Curveball' = 'darkgreen', 'Sinker' = '#a34700',  'Slider'='#33A8FF',
                                 'Cutter' = 'gold',  'Changeup'='violet', 'Other' = 'black', 'Splitter' = 'black', 'Knuckleball' = 'black')) +
    theme_void()+
    geom_text(aes(label = `#`), color = 'white', fontface = 'bold', size = 4.5)+
    theme(
      strip.background = element_rect(fill = "#12294b", color = "#12294b"),
      strip.text = element_text(color = "white", size = 10),
      legend.position = 'none',
      legend.direction = "horizontal"
    )
  
  pa_bb_plot <-ggplot()+
    geom_mlb_stadium(stadium_ids = 'cubs',
                     stadium_transform_coords = TRUE,
                     stadium_segments = c('home_plate', 'foul_lines', 'infield_outer', 'infield_inner') ,
                     size = 1,
                     color = 'black')+
    
    geom_segment(data = of_wall, aes(x = Start_x,y=Start_y, xend = End_x, yend = End_y), size = 1, color = 'black')+
    geom_point(data = pa_track %>% filter(PitchCall == 'InPlay'), aes(x = hc_x, y = hc_y, fill = PlayResult), pch = 21, size = 5, color = 'black')+
    scale_fill_manual(values = c('1B' = '#ff4a65', '2B' = '#785EF0', '3B' = '#FFB000',  'HR'='forestgreen', 'Out' = 'black',
                                 'E' = 'purple',  'FC'='lightgrey', 'SAC' = 'darkgrey')) +
    xlim(-275,275)+
    ylim(-35,450)+
    coord_equal()+
    theme_void()+
    theme(plot.title = element_text(hjust = .5, face = 'bold', color = 'black'),
          plot.subtitle = element_text(hjust = .5, face = 'bold', color = 'black'),
          legend.position = 'none')
  
  
  print(
    kable(pa_flex%>% 
            mutate(across(c(EV, LA, Dist, VB,HB,Spin,Tilt,Velo), ~ ifelse(is.na(.), "", .)))%>%  
            mutate(Pitch = as.character(paste(Pitch))), format = "latex", linesep = "") %>%
      kable_styling(latex_options = "HOLD_position", position = "center", font_size = 11) %>%
      column_spec(1, bold = TRUE, border_left = TRUE) %>%
      row_spec(0, color = "white", background = "#12294b") %>%
      column_spec(ncol(pa_flex), border_right = TRUE) %>%
      add_header_above(setNames(ncol(pa_flex), caption), bold = TRUE, background = "#12294b", color = "white") %>%
      # add_header_above(c(" " = ncol(pa_flex)), bold = TRUE) %>%
      column_spec(2, bold = TRUE, color = "white",
                  background = case_when(
                    pa_flex$Pitch == 'FB' ~ 'red',
                    pa_flex$Pitch == 'SI' ~ '#a34700',
                    pa_flex$Pitch == 'CT' ~ '#FFD700',
                    pa_flex$Pitch == 'CB' ~ '#228b22',
                    pa_flex$Pitch == 'SL' ~ '#33A8FF',
                    pa_flex$Pitch == 'CH' ~ '#E398F7',
                    pa_flex$Pitch == 'KN' ~ 'black',
                    pa_flex$Pitch == 'SPL' ~ 'black',
                    TRUE ~ 'darkgrey'
                  )
      ) 
  )
  cat("\\vspace{-10mm}")
  grid.arrange(pa_zone_plot, pa_bb_plot, nrow = 1)
  cat("\\vspace{-10mm}")
  cat("--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------")
  # cat("___") 
}

```